### 2012-03-27 exam4/2.tex
Space.

\noindent\begin{minipage}{8cm}\sloppy
\begin{itemize}
\item All problems on this exam are in Java. You may use the the
  primitives and expression forms of Java, and the libraries we have
  used in class and in lab; anything else must be defined.

>>>>

\noindent\begin{minipage}{8cm}\sloppy
\begin{itemize}
\item All problems must be done in Java. You may use any Java we have
  used in class and in lab; anything else must be defined.
